\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{multicol}
\usepackage{tgpagella}
\begin{document}

\begin{center}
\LARGE{{\textbf{\textsf{}Project Proposal\textbf{}}}}
\end{center}

\begin{center}
\Large{\texttt{CSE311 - Database Management System}}
\end{center}

\begin{center}
\large MD. Mehedi Hasan - \large 1812624642
\end{center}

\section*{Introduction}

A buyer always wants to get the best value for money. They always want to learn about the product they are buying. But it is not an easy task for a seller to remember the specifications of all products at the same time. \\
A website can break the barrier for both of them. Not only a buyer can easily study and compare products but also the work of the seller also gets reduced.

\section*{Objectives}
\begin{itemize}
\item  Create a database containing all products. 
\item  Create tables containing all attributes of an item. 
\item  Provide registration and login system for users.
\item  Create an optimized and user-friendly interface.
\end{itemize}

\section*{Target}
\begin{itemize}
\item  People who want to learn about components
\item  A customer who wants to select components sitting at home
\item  A customer from a remote area who wants to buy components through Internet
\end{itemize}

\section*{Value Proposition}
This website will help the seller as well as customers at the same time. The seller will be more productive as the website will help him to save more time. Customers will be more satisfied as they will get the chance to learn and select the best product according to their budget.

\section*{Features}
\begin{itemize}
\item  A registered user will be able to save his desired item in \textbf{Cart}.
\item  An embedded \textbf{map} to help people can find the shop easily.
\item  A \textbf{newsletter} system to notify people about recent products \\ 
\textit{*(More features will be added if possible)}
\end{itemize}

\section*{Tools and Resources}
\begin{itemize}
\begin{multicols}{2}
\item  HTML / CSS
\item  Bootstrap
\item  Javascript
\item  PHP
\item  MySQL
\item  Google Map API
\end{multicols}
\end{itemize}
\section*{Challenge} 
The biggest challenge of this project is that I will not be able to use my prior languages or skills. I have to learn new languages as well as implement them in the project at the same time.As I chose to do all the work by myself, I have to spend quality time almost every day on this project.

\end{document}
